Making Q-learning robust to time discretization

### 2019-01-17 paper/icml_drau/relatedworks.tex

\TODO{Say that Actor-critic has no problem when $\deltat\to 0$? With SGD
but not with RMSProp, and needs robust exploration}

@@

Reinforcement learning has been studied from a mathematical perspective
when time and space are both continuous, in connection with optimal
control and the Hamilton--Jacobi--Bellman (HJB) equation (a PDE which
characterizes the value function for continuous space-time). Continuous
space-time algorithms are studied in
\cite{cont_rl,MunosBourgines98} (see also the references therein).
\cite{MunosBourgines98} use a grid approach to provably solve the HJB
equation when discretization tends to $0$ (assuming every state in the
grid is visited a large number of times). However,
the corresponding algorithms are
often impractical \cite{cont_rl} for larger-dimensional problems.
\cite{cont_rl} focusses on practical algorithms specific to the continuous
space-time case, including advantage updating.

>>>>

\TODO{Somewhere else: Say that Actor-critic has no problem when $\deltat\to 0$? With SGD
but not with RMSProp, and needs robust exploration}

@@

Reinforcement learning has been studied from a mathematical perspective
when time and space are both continuous, in connection with optimal
control and the Hamilton--Jacobi--Bellman (HJB) equation (a PDE which
characterizes the value function for continuous space-time). Continuous
space-time algorithms are studied in
\cite{cont_rl,MunosBourgines98} (see also the references therein).
\cite{MunosBourgines98} use a grid approach to provably solve the HJB
equation when discretization tends to $0$ (assuming every state in the
grid is visited a large number of times). However,
the corresponding algorithms are
impractical \cite{cont_rl} for larger-dimensional problems.
\cite{cont_rl} focusses on practical algorithms specific to the continuous
space-time case, including advantage updating.
